\subsection{Other Information}

An account that has type "USER" can perform INSERT, UPDATE AND DELETE of an order or a favourite item via the interface. It can also perform the UPDATE on the account table to change the values of its attributes.

An account of type "ADMIN" can do the INSERT and the UPDATE on circuit and car tables. Additionally, it can do the same operation in carType and circuitType. Finally, it can INSERT and DELETE a new mapping between a carType and a circuitType.

The insertion operation in order table is protected by a function that is triggered before the insert command. The function checks if the circuit and the car associated with the new order are in a consistent status with respect to the suitability between a type of car and a type of circuit. This is performed by checking whether a row exists in carCircuitSuitability table which refers to the selected types. If the function returns a positive result, then the insertion is performed, otherwise an error will be thrown. In this function it is also checked if the price corresponds to the product of the number of laps and the price for a single lap.

There are some other controls in car and circuits tables to prevent that the user inserts some non valid values (e.g a negative horsepower in car or a negative length in circuit). It also checks if the order price corresponds to the product between the cost of a single lap and the number of laps.

An user can make multiple orders on the same date, but the function checks if all those orders contains the same circuit. This is designed to avoid possible logistical problems in the situation where the user books two circuits that are far apart.