\section{Main Functionalities}
%What are the main functionalities of the web app? what services does it offer and how it is organized?


WaCar is an intuitive online platform catering to two primary user groups: administrators and users. Upon landing on WaCar's homepage, users are greeted with an array of features and options designed to streamline their experience. Firstly, users can effortlessly see a comprehensive list of available cars and circuits, each accompanied by detailed descriptions to aid in their selection process. Concurrently, users are presented with the option to either login or register on the platform, providing essential details like name, surname, email, and password to unlock access to the platform's full suite of features.

Once registered, users can seamlessly proceed to place orders via a dedicated subsection of the web application. Here, users can select their desired car from various categories, ranging from supercars to off-road vehicles, with each category offering a diverse range of brands and models. Following car selection, users then choose a compatible circuit and specify the number of laps for their session.

The next step involves selecting a suitable time slot from the available options. Once a preferred time slot is chosen, users are presented with a preview of their order, affording them the opportunity to confirm or cancel the booking as desired. Additionally, users have the capability to manage their orders, including the option to delete them, and access a comprehensive history of past orders for reference purposes.

Furthermore, users can mark favorite circuits and cars for expedited access in the future, ensuring their preferred selections are prominently displayed at the top of the page during subsequent visits to the platform. On the administrative side, administrators oversee the management of tracks and cars, with responsibilities including adding, removing, and modifying them as needed. Administrators also possess the authority to adjust pricing for laps, cars, and tracks, in addition to managing time slots to ensure efficient operation of the platform.